Reply to reviewers

### 2025-01-03 review/reply.Rmd
my responses

\textcolor{purple}{We have added numbering to the main equations such that they can be referenced in the explanations, this should make the derivation easier to follow. XXX to check @Annalisa}

@@

\textcolor{purple}{We have numbered the main equations and now use referencing in the description. XXX check flow of content @Annalisa}

@@

\textcolor{purple}{XXX todo @Annalisa}

>>>>

\textcolor{purple}{We have added numbering to the main equations such that they can be referenced in the explanations, this should make the derivation easier to follow. More detail has been added to the theorem and proof in section 3.}

@@

\textcolor{purple}{We have numbered the main equations and now use referencing in the description. Segments of this section have been rewritten to include more explanation and enhance flow, and variables have been defined earlier, before they are used.}

@@

\textcolor{purple}{The ellipsoid equation is now specifically referenced in the statement of the theorem. The mentioned variables are now defined before the statement of the theorem, helping reorganise the section to improve clarity. Although the proof is not fundamentally restructured, it has been reworded with further explanation added.}
